%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{setspace}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{0in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{0pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{0pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\centerline{\textbf{\huge Michael Guan}}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  607-379-7339 & {www.linkedin.com/in/mikeguan1999}\\
mhg99@cornell.edu & mikeguan1999@gmail.com\\
\end{tabular*}

%-----------Summary-----------------

\section{Summary}

Highly responsible individual with an excellent work ethic looking for a part-time job. Organized and enthusiastic in and out of the work place. Quick learner that is very detail-oriented and driven.


%-----------Skills-----------------

\section{Highlights}

 \resumeSubHeadingListStart

    \resumeSubItem{Soft Skills}
      {Excellent Communication Skills, Great Time Management, Highly Responsible, Trained in CPR and First Aid}
    \resumeSubItem{Hard Skills}{Computer Technologies, Microsoft Office, Proficient in Chinese and English}
  \resumeSubHeadingListEnd



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Coding4Youth}{Cupertino, CA}
      {Computer Science Instructor}{May 2019 - Sep. 2019}




      \resumeItemListStart
        \resumeItem{Computer Science Tutor}
		{Taught students the fundametals of Java and Python using a structured curriculum and was responsible for giving lectures as well as assigning homework and project assignments.}
      \resumeItemListEnd

 \resumeSubheading
      {Country Club of Ithaca}{Ithaca, NY}
      {Lifeguard}{May. 2016 - Aug. 2018}
      \resumeItemListStart
        \resumeItem{Country Club Pool Lifeguard}
          {Ensured the safety and liveliness of customers at the Country Club Pool. Responsible for enforcing and explaining the pool rules and maintaining the cleanliness and orderliness of the pool area.}
	\resumeItem{Swim Instructor}
		{Taught the basic forms of swimming techniques including the Front Crawl and Backstroke to the kids at the Summer Adventure Program.}
      \resumeItemListEnd


\resumeSubheading
	{Sciencenter}{Ithaca, NY}
	{Volunteer}{May. 2014 - Sep. 2018}
	\resumeItemListStart
		\resumeItem{Interactive Floor Programs}
			{Demonstrated different scientific properties and experiments through a variety of fun and engaging activities. The subjects for these activities rotates every few weeks. }
		\resumeItem{Discovery Room}
			{Helped younger kids explore the different topics of science through discovery boxes: activities that cover many fields of science, including astronomy, math, engineering, and biology. }

\resumeItemListEnd

  \resumeSubHeadingListEnd


%%-----------PROJECTS-----------------
%\section{Projects}
%  \resumeSubHeadingListStart
%    \resumeSubItem{Marble Sorter}
%      {Built a device that uses VEX\textsuperscript{\textregistered}  motors and light sensors as well as 3d printed parts that sorts glass marbles based on color.}
%    \resumeSubItem{Critter World}
%	{ Implemented in a group of three people a Java program to simulate artificial life and behaviors. This project included the construction of an interpreted language to help create ``critters'' with different traits and behaviors and a graphical user interface to help visualize and interact with the critter world. }
%    
%    \resumeSubItem{Pok\'emon Project} 
%      {Created a program in Python that utilizes machine learning algorithms to predict the type of a Pok\'emon based on its base statistics (Attack, Defense, HP, Speed, etc.)}
%
% \resumeSubItem{Chess Game}
%      {Implemented a chess application using functional programming(OCaml) and the Graphics GUI package to allow two human players to play the standard game of chess.}
%  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cornell University}{Ithaca, NY}
      {College of Engineering Class of 2022; Cumulative GPA: 3.98 }{Aug. 2018 -- May. 2022}\\
 \resumeItemListStart
	\resumeSubItem{Major}{B.S. in Computer Science}
	\resumeSubItem{Minor}{Double Minor in Electrical/Computer Engineering and Game Design}
 \resumeItemListEnd
    \resumeSubheading
      {Ithaca High School}{Ithaca, NY}
      {Class of 2018; GPA: 4.17}{Sep. 2014 -- June. 2018}
 \resumeItemListStart
	\resumeSubItem{Extracurriculars}{Captain of Science Olympiad, Vice President of Math Club, and an avid member of Dev Team and the Varsity Swim Team}
	\resumeSubItem{Awards}{First Place Science Olympiad Regionals, New Your State Math League Team Top Scorer, AP+PLTW Student Achievement in Engineering, PTA Award for Science and Technology}
 \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}
